Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators

### 2019-09-17 PaperMagneticProfiles_JBSMSE.tex
Edit section on results of IT x RC.
In particular, the "same average" comparison was removed.

When comparing the \textcolor{black}{performances resulting from the application of the different} magnetic profiles, the average magnetic field during the hot cycle \textcolor{black}{will be considered} the same; this implies a higher peak for the rectified cosine. For the cold cycle, two comparison methods are considered, as shown in \autoref{fig:comparison-methods-profiles}:

\begin{enumerate}
\item The minimum values for both profiles is the same;
\item The average value for both profiles during the cold cycle is the same.
\end{enumerate}

\textcolor{black}{For} reference, in all simulations,  the minimum value for the rectified cosine was fixed at ${B}\ped{min,RC} = \SI{0.1}{\tesla}$. \textcolor{black}{In} the first comparison, the minimum value for the instantaneous \textcolor{black}{waveform} was kept at the same level (${B}\ped{min,IT} =  {B}\ped{min,RC}$); hence, the average low value for the RC profile was higher ($\average{B}\ped{low,RC} > \average{B}\ped{low,IT}$). This represents common design scenarios: a constant low-valued plateau for the magnetic field for instantaneous-like magnetic profiles \cite{bib:insinga16_optim,bib:benedict16_desig}, or a low peak for the rectified cosine profile \cite{bib:trevizoli15_desig_halbac}.  For the other comparison method, the low level of the instantaneous profile was increased (${B}\ped{min,IT} >  {B}\ped{min,RC}$) \textcolor{black}{in order} to keep the \textcolor{black}{same} average ($\average{B}\ped{low,RC} = \average{B}\ped{low,IT}$).

\begin{figure}[!ht]
  \centering
  \subfloat[Same minimum]{\includegraphics[width=8cm]{profiles_it_and_rc_same_minimum}\label{fig:profiles_inst_cos_same_minimum}}
\quad
  \subfloat[Same average]{\includegraphics[width=8cm]{profiles_it_and_rc_same_average}\label{fig:profiles_inst_cos_same_average}}
  \caption{Comparison methods for the instantaneous and rectified cosine profiles }
  \label{fig:comparison-methods-profiles}
\end{figure}

In addition, simulations were \textcolor{black}{carried out} for various values of blow fraction; the rectified cosine profile can benefit from a smaller blow fraction because this can concentrate the flow during the periods of very high or low fields. In this section, all results use the critical value of blow fraction that maximized the cooling capacity: fluid flowing during the entire period for the instantaneous profile, and only during \SI{60}{\percent}  of the period (the smallest blow fraction tested) for the cosine profile; this latter case is shown in \autoref{fig:cos-inst-60}.

@@

Figure~\ref{fig:cos_ins} shows the cooling capacity attained by the device at a frequency of \SI{1}{\hertz} and different utilizations, for both comparison methods. The horizontal axis shows the average value during the high field region. 
\textcolor{black}{For} Fig.~\ref{fig:comp_min}, the instantaneous profile almost always yields a higher performance, while for Fig.~\ref{fig:comp_avg} the rectified cosine profile generates higher cooling capacities. Since the average \textcolor{black}{field} during the hot cycle (high field stage) is the same, the main difference is due to the low magnetic field levels. For the ``same minimum'' comparison, the instantaneous profile is capable of keeping the magnetic field at low levels for the whole half-cycle, which is beneficial for performance;  for $\Phi=1.0$ and $\average{B}\ped{high} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile.  As demonstrated by \cite{bib:asme-mce}, a higher average magnetic field during the low-field stage increases the solid temperature and consequently results in  warmer fluid entering the cold heat exchanger, representing a thermal loss. In the ``same-average'' comparison, the cosine profile is capable of achieving much lower levels (since its minimum value is fixed), therefore providing more cooling power. However, as explained before, this \textcolor{black}{analysis serves mainly the purpose of illustrating the influence of low magnetic field variation, by looking at two hypothetical scenarios. More} complex \textcolor{black}{magnetic circuit}  geometries \textcolor{black}{are} required to generate the instantaneous magnetic profile \textcolor{black}{with a} low \textcolor{black}{magnetic field} close to 0.

\begin{figure}[!ht]
  \centering
  \subfloat[Same minimum]{\includegraphics[width=8cm]{Qc_B_comp_f_1_same_minimum}\label{fig:comp_min}}
\,
%  \subfloat[Same average]{\includegraphics[width=8cm]{Qc_B_comp_f_1_same_low_average}\label{fig:comp_avg}}
\,
  \caption{Cooling capacity as a function of the  average high magnetic field, for different utilizations. \textcolor{black}{``IT''}: instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}), for both comparison methods.}
 \label{fig:cos_ins}
\end{figure}

The only exception in the ``same minimum'' comparison is seen for the lowest utilization of $\Phi = 0.2$, where the performance is slightly better for the RC profile. Since the blow fraction for the cosine is lower, the mass flow rate \textcolor{black}{is} higher \textcolor{black}{in the latter for} the same utilization (cf. Eq.~\eqref{eq:200}). \textcolor{black}{This} increases \textcolor{black}{the} heat transfer rate, as previously explained ---  outweighing the effects of the magnetic field.

The same analysis, but in terms of the coeficient of performance, is shown in \autoref{fig:cos_ins_cop}. For the ``same average'' analysis, the $\cop$ results show the same trends as the cooling capacity. However, for the \textcolor{black}{somewhat} more realistic analysis where the minimum of both profiles are the same, the rectified cosine profile yields better results for small values of utilization. This is due to \textcolor{black}{a} lower pumping power, as the mass flow rate for the cosine profile is slightly higher, but also flows for a shorter period of time. \textcolor{black}{Since} in this region the cooling capacity for the RC profile can be close to or higher than the \textcolor{black}{IT} profile (cf. Fig.~\autoref{fig:comp_min}), the coefficient of performance becomes higher for the rectified cosine profile.

\begin{figure}[!ht]
  \centering
  \subfloat[Same minimum]{\includegraphics[width=7cm]{COP_B_comp_f_1_same_minimum}\label{fig:comp_min_cop}}
\,
%  \subfloat[Same average]{\includegraphics[width=7cm]{COP_B_comp_f_1_same_low_average}\label{fig:comp_avg_cop}}
\,
  \caption{Coefficient of performance as a function of the  average high magnetic field, for different utilizations. \textcolor{black}{``IT''}: instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}), for both comparison methods.}
 \label{fig:cos_ins_cop}
\end{figure}

@@

As shown in the previous section, the instantaneous profile \textcolor{black}{generally} yields the highest values \textcolor{black}{of} cooling capacity. Therefore, in this section, a more detailed analysis of \textcolor{black}{this} profile has been carried out, \textcolor{black}{where the} maximum field in \autoref{fig:cobem-profiles} \textcolor{black}{is} varied, while the minimum value is kept at \SI{0.05}{\tesla}. Figure~\ref{fig:qc_phi_inst} shows the cooling capacity as a function of \textcolor{black}{the} utilization, for several levels of the maximum magnetic field \textcolor{black}{and} two different operating frequencies. Because of the conflict between a low heat transfer rate for flow rates \textcolor{black}{that are} too low and losses in regenerator effectiveness in flow rates \textcolor{black}{that are} too high, there are critical values of utilization that maximize \textcolor{black}{the} cooling capacity, and this critical values increases with the magnetic field. \textcolor{black}{For} higher magnetic fields, the increase in the MCE surpasses the loss of effectiveness, and one can go to higher flow rates without losing performance. It can also be seen in Fig.~\ref{fig:qc_phi_inst} that at  higher frequencies the values of cooling power are higher, and also the critical values of utilization are lower; however, this \textcolor{black}{is} usually achieved at the \textcolor{black}{expense} of \textcolor{black}{a} higher power consumption in AMR devices at higher frequencies \cite{bib:lei15_study,NIKNIA2016601}.

@@

The parameters in \autoref{tab:params-cobem} were chosen from preliminary simulations, \textcolor{black}{so} they are not  optimal. To understand the impact of \textcolor{black}{the} regenerator geometry on the performance with the instantaneous profile, the regenerator height was varied in Fig.~\ref{fig:Qc_H_inst}, and all other parameters from \autoref{tab:params-cobem} were kept fixed and with $\phi=0.4$. As expected, higher magnetic fields allow for smaller regenerators (hence more compact systems) to achieve a \textcolor{black}{desired} cooling capacity. For instance, to achieve a capacity of \SI{100}{\watt}, increasing the field from \num{1.0} to \SI{1.2}{\tesla} \textcolor{black}{results} in regenerators \textcolor{black}{that are} \SI{36}{\percent} smaller. Comparing results \textcolor{black}{for} cooling capacity and coefficient of performance, the trends are largely the same, as the former is more sensitive to variations in the magnetic field and regenerator height than the components of power.

>>>>

When comparing the \textcolor{black}{performances resulting from the application of the different} magnetic profiles, the average magnetic field during the hot cycle \textcolor{black}{will be considered} the same; this implies a higher peak for the rectified cosine. For the cold cycle,  the minimum values for both profiles is the same, as shown in \autoref{fig:comparison-methods-profiles}. \textcolor{black}{For} reference, in all simulations,  the minimum value for the rectified cosine was fixed at ${B}\ped{min} = \SI{0.1}{\tesla}$.

\begin{figure}[!ht]
  \centering
\includegraphics[width=8cm]{profiles_it_and_rc_same_minimum}
  \caption{Configuration of average and extrema values of the instantaneous and rectified cosine profiles }
  \label{fig:comparison-methods-profiles}
\end{figure}

Simulations were \textcolor{black}{carried out} for various values of blow fraction; the rectified cosine profile can benefit from a smaller blow fraction because this can concentrate the flow during the periods of very high or low fields. In this section, all results use the critical value of blow fraction that maximized the cooling capacity: fluid flowing during the entire period for the instantaneous profile, and only during \SI{60}{\percent}  of the period (the smallest blow fraction tested) for the cosine profile; this latter case is shown in \autoref{fig:cos-inst-60}.

@@

Figure~\ref{fig:cos_ins} shows the cooling capacity attained by the device at a frequency of \SI{1}{\hertz} and different utilizations. The horizontal axis shows the average value during the high field region. The instantaneous profile almost always yields a higher performance, and cince the average \textcolor{black}{field} during the hot cycle (high field stage) is the same, the main difference is due to the low magnetic field levels. For the ``same minimum'' comparison, the instantaneous profile is capable of keeping the magnetic field at low levels for the whole half-cycle, which is beneficial for performance;  for $\Phi=1.0$ and $B\ped{high} = \SI{1.40}{\tesla}$, the cooling capacity for the instantaneous profile is $\SI{196.3}{\percent}$ higher than for the cosine profile.  As demonstrated by \cite{bib:asme-mce}, a higher average magnetic field during the low-field stage increases the solid temperature and consequently results in  warmer fluid entering the cold heat exchanger, representing a thermal loss.

\begin{figure}[!ht]
  \centering
\includegraphics[width=8cm]{Qc_B_comp_f_1_same_minimum}
  \caption{Cooling capacity as a function of the  average high magnetic field, for different utilizations. \textcolor{black}{``IT''}: instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}).}
 \label{fig:cos_ins}
\end{figure}

The only exception in this comparison  is seen for the lowest utilization of $\Phi = 0.2$, where the performance is slightly better for the RC profile. Since the blow fraction for the cosine is lower, the mass flow rate \textcolor{black}{is} higher \textcolor{black}{in the latter for} the same utilization (cf. Eq.~\eqref{eq:200}). \textcolor{black}{This} increases \textcolor{black}{the} heat transfer rate, as previously explained ---  outweighing the effects of the magnetic field.

The same analysis, but in terms of the coeficient of performance, is shown in \autoref{fig:cos_ins_cop}, with the same trends as for the cooling capacity; however, in this case  the rectified cosine profile yields better results for small to medium values of utilization. This is due to \textcolor{black}{a} lower pumping power, as the mass flow rate for the cosine profile is slightly higher, but also flows for a shorter period of time. \textcolor{black}{Since} in this region the cooling capacity for the RC profile can be close to or higher than the \textcolor{black}{IT} profile (cf. Fig.~\autoref{fig:comp_min}), the coefficient of performance becomes higher for the rectified cosine profile.

\begin{figure}[!ht]
  \centering
\includegraphics[width=7cm]{COP_B_comp_f_1_same_minimum}
  \caption{Coefficient of performance as a function of the  average high magnetic field, for different utilizations. \textcolor{black}{``IT''}: instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}).}
 \label{fig:cos_ins_cop}
\end{figure}

@@

As shown in the previous section, the instantaneous profile \textcolor{black}{generally} yields the highest values \textcolor{black}{of} cooling capacity. Therefore, in this section, a more detailed analysis of \textcolor{black}{this} profile has been carried out, \textcolor{black}{where the} maximum field  \textcolor{black}{is} varied, while the minimum value is kept at \SI{0.05}{\tesla}. Figure~\ref{fig:qc_phi_inst} shows the cooling capacity as a function of \textcolor{black}{the} utilization, for several levels of the maximum magnetic field \textcolor{black}{and} two different operating frequencies. Because of the conflict between a low heat transfer rate for flow rates \textcolor{black}{that are} too low and losses in regenerator effectiveness in flow rates \textcolor{black}{that are} too high, there are critical values of utilization that maximize \textcolor{black}{the} cooling capacity, and this critical values increase with the magnetic field. \textcolor{black}{For} higher magnetic fields, the increase in the MCE surpasses the loss of effectiveness, and one can go to higher flow rates without losing performance. It can also be seen in Fig.~\ref{fig:qc_phi_inst} that at  higher frequencies the values of cooling power are higher, and also the critical values of utilization are lower; however, this \textcolor{black}{is} usually achieved at the \textcolor{black}{expense} of \textcolor{black}{a} higher power consumption in AMR devices at higher frequencies \cite{bib:lei15_study,NIKNIA2016601}.

@@

The geometric parameters in \autoref{tab:params-cobem} were chosen from preliminary simulations, \textcolor{black}{so} they are not  optimal. To understand the impact of \textcolor{black}{the} regenerator geometry on the performance with the instantaneous profile, the regenerator height was varied in Fig.~\ref{fig:Qc_H_inst}, and all other parameters from \autoref{tab:params-cobem} were kept fixed and with $\phi=0.4$. As expected, higher magnetic fields allow for smaller regenerators (hence more compact systems) to achieve a \textcolor{black}{desired} cooling capacity. For instance, to achieve a capacity of \SI{100}{\watt}, increasing the field from \num{1.0} to \SI{1.2}{\tesla} \textcolor{black}{results} in regenerators \textcolor{black}{that are} \SI{36}{\percent} smaller. Comparing results \textcolor{black}{for} cooling capacity and coefficient of performance, the trends are largely the same, as the former is more sensitive to variations in the magnetic field and regenerator height than the components of power.
